A 30 Million Year Old Mini-Neptune in the Kepler Field

### 2021-05-27 paper/ms.tex
update ms

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded transit of Kepler 1627b, with stellar
    variability removed.}  
    The 1-$\sigma$ model uncertainties and the median model are shown
    as the faint purple band, and the dark purple line.
    Gray points are individual \texttt{PDCSAP} flux measurements;
    black points are binned to 20 minutes, with a representative error
    bar shown.
		\label{fig:phasefold}
	}
\end{figure*}

@@

@@

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded transit of Kepler 1627b, with stellar
    variability removed.}  
    The 1-$\sigma$ model uncertainties and the mean model are shown
    as the faint purple band, and the dark purple line.
    Gray points are individual \texttt{PDCSAP} flux measurements;
    black points are binned to 20 minutes, with a representative error
    bar shown.
    {\bf LGB FIXME: seems like the uncertainty is bigger than the RMS
    in the out of transit...}
		\label{fig:phasefold}
	}
\end{figure*}

@@

Figure~\ref{fig:phasefold} shows X, Y, Z.  The residuals during the
transit may hint at some small degree of unfitted signal -- in the
sense that the observations are systematically high in the first half
of transit, and low in the second half.  
One possible explanation could be that we are seeing the effects of
gravity darkening (e.g., CITE Masuda 2015).
The expected amplitude of the effect is XXX, based on CITE.
However, there is also a dip of comparable amplitude shortly before
the transit. 
Given the uncertainties in the stellar variability model, we expect
that these patterns may correspond to more noise than signal.

@@

\section{Bonus figures that wont be included}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{dontinclude0.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf corner plot of gptransit fit}
	}
\end{figure*}
